---
output:
  pdf_document:
    citation_package: natbib
    latex_engine: pdflatex
    toc: true
    toc_depth: 2
    includes:
        in_header: vignette_head.tex
    keep_tex: true
title: "Multiple Treatment Effects Regression"
author: "Michal Kolesár"
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
bibliography: library.bib
fontsize: 11pt
vignette: >
  %\VignetteIndexEntry{multe}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE, cache=FALSE}
library("knitr")
knitr::opts_knit$set(self.contained = FALSE)
knitr::opts_chunk$set(tidy = TRUE, collapse=TRUE, comment = "#>",
                      tidy.opts=list(blank=FALSE, width.cutoff=55))
```

The package `multe` implements contamination bias diagnostics for regressions
with multiple treatments developed in @ghk23. This vignette illustrates the
methods using data from @FrLe13.

First, we fit a regression of test scores on a race dummy (treatment of
interest) and a few controls, weighting using sampling weights:

```{r setup}
library("multe")
## Regression of IQ at 24 months on race indicators and baseline controls
r1 <- stats::lm(std_iq_24~race+factor(age_24)+female+SES_quintile,
                weight=W2C0, data=fl)
## Compute alternatives estimates free of contamination bias
m1 <- multe(r1, "race", cluster=NULL)
print(m1, digits=3)
```

The package reports five different estimators:

1. PL: The uninteracted regression estimator based on the partially linear (PL)
   model.
2. OWN: The own-treatment effect component of the contamination bias
   decomposition. If OWN is close to PL, as above, this indicates negligible
   contamination bias.
3. ATE: The unweighted average treatment effect, implemented using regression
   that interacts the treatment dummies with the controls.
4. EW: Weighted ATE estimator based on easiest-to-estimate weighting (EW)
   scheme, implemented by running one-treatment-at-a-time regressions.
5. CW: Weighted ATE estimator using easiest-to-estimate common weighting (CW)
   scheme from Corollary 2 in @ghk23, implemented using weighted regression.

Precise definitions of these estimators are given in the Methods section below.

In this example, the propensity score varies significantly with covariates, as
indicated by the p-values of the Wald and LM tests.

Including many controls may result in overlap failure, as the next example demonstrates:

```{r r2}
r2 <- stats::lm(std_iq_24~race+factor(age_24)+female+SES_quintile+
                    factor(siblings)+family_structure, weight=W2C0, data=fl)
m2 <- multe(r2, treatment="race")
print(m2, digits=3)
```

The issue is that no observations with 6 siblings have race equal to `other`:

```{r r3}
table(fl$race[fl$siblings==6])
```

Thus, the ATE estimator comparing `other` to `white` is not identified. The
package drops observations with 6 siblings from the sample to form an "overlap
sample" (see Methods section below for precise construction of this sample),
where the all estimators are identified.

For a researcher who wants to check whether there is a significant difference
between the PL estimator and the other estimators, the data frame `cb_f` reports
the difference between the estimates in the full sample, along with the
corresponding standard error. The data frame `cb_o` reports the differences and
standard errors for the overlap sample:

```{r r4}
print(m2$cb_f, digits=3)
print(m2$cb_o, digits=3)
```

We see statistically significant difference between the OWN and PL estimate
(i.e. significant contamination bias) for all races, both in the full sample and
in the overlap sample.

## Standard errors

The package also computes "oracle" standard errors, in addition to the usual
standard errors reported above. These can be accessed in the data frame `est_f`
(or `est_o` for the overlap sample results)

```{r r5}
print(m1$est_f, digits=3)
```

These oracle standard errors (`oracle_se`) don't account for estimation error in
the propensity score, in contrast to the default standard errors (`pop_se`), see
Methods section below.

Specifying the `cluster` argument allows for computation of clustered standard
errors:

```{r r6}
## cluster in interviewer ID
m1alt <- multe(r1, "race", cluster=factor(factor(fl$interviewer_ID_24)))
print(m1alt, digits=3)
```


# Methods

This section describes the implementation of the bias decomposition formula and
the implementation of alternative estimators. Relative to @ghk23, we
generalize the setup to allow for sampling weights $\omega_{i}^{2}$ (setting the
sampling weights to one recovers unweighted formulas). We also explicitly deal
with overlap issues.

We are interested in the effect of treatment $D_{i}\in\{0,1,\dotsc, K\}$ on an
outcome $Y_{i}$. Let $X_{i}=\1{D_{i}=1,\dotsc, D_{i}=K}$ denote a vector of
treatment indicators, let $X_{i0}=\1{D_{i}=0}$, and let $Z_{i}=(1,W_{i}')'$
denote a vector of controls, including an intercept. We focus on the case where
the controls enter linearly, so that control functions take the form
$\mathcal{G}=\{z'\gamma\colon \gamma\in\mathbb{R}^{1+\dim(W_i)}\}$.

We assume that $\mu_{k}(W_i):=E[Y_{i}(k)\mid W_{i}]\in\mathcal{G}$, so that we may
write $\mu_{k}(W_{i})=W_{i}'\alpha_{k}$ for some vectors $\alpha_{k}$,
$k=0,\dotsc, K$. The average treatment effect (ATE) conditional on $W_{i}$ is
then given by $\tau(W_{i})=Z_{i}'(\alpha_{k}-\alpha_{0})$, and $\alpha_{k}$
correspond to the coefficients in the interacted regression
\begin{equation}
  Y_{i}=\sum_{k=0}^{K}X_{ik}Z_{i}'\alpha_{k}+\dot{U}_{i}\label{eq:linear_mu},
    % =Z_{i}'\alpha_{0}+\sum_{k=1}^{K}X_{ik}Z_{i}'\gamma_{k}\label{eq:linear_gamma}
    % &=\alpha_{0, k}+W_{i}'\alpha_{W, 0}+\sum_{k=1}^{K}X_{ik}\tau_{k}+\sum_{k=1}^{K}X_{ik}(W_{i}-E[W_{i}])'\gamma_{W, k}.
    %   \label{eq:linear_tau}
\end{equation}
with $\dot{U}_{i}$ conditionally mean zero. The uninteracted partially linear
(PL) estimator is given by estimating
\begin{equation}\label{eq:uninteracted_linear}
    Y_i=\sum_{k=1}^{K} X_{ik}\beta + Z_i'\phi +U_{i},
\end{equation}
by weighted least squares (WLS), yielding
$\hat{\beta}=(\sum_{i}\omega_{i}^{2}\dot{X}_{i}\dot{X}_{i}')^{-1}\sum_{i}\omega_{i}^{2}\dot{X}_{i}Y_{i}$,
where $\dot{X}$ is the sample residual from WLS regression of $X_{i}$ onto
$Z_{i}$. By Proposition 1 in @ghk23, the population analog of $\hat{\beta}$,
$\beta$, has the decomposition
\begin{equation*}
  \beta=E[\diag(\Lambda_{i})\tau(W_{i})]+E[\Lambda_{i}-\diag(\Lambda_{i})\tau(W_{i})],
\end{equation*}
where
$\Lambda_{i}=E[\tilde{X}_{i}\tilde{X}_{i}']^{-1}E[\tilde{X}_{i}X_{i}\mid
W_{i}]$, and $\tilde{X}_{i}$ is the population analog of $\dot{X}_{i}$, the
population residual from regressing $X_{i}$ onto $W_{i}$. Let $\hat{\alpha}_{k}$
denote the WLS estimates based on \eqref{eq:linear_mu}. By construction, the
sample residuals from estimating \eqref{eq:linear_mu} and $Z_{i}$ are both
orthogonal to $\dot{X}_{i}$. As a result, we obtain the exact decomposition
\begin{equation}\label{eq:1}
  \begin{split}
    \hat{\beta}
    &=E_{n}[\dot{X}_{i}\dot{X}_{i}']^{-1}E_{n}[\dot{X}_{i}Y_{i}]=
      % E_{n}[\dot{X}_{i}\dot{X}_{i}']^{-1}
      % E_{n}[\dot{X}_{i}\sum_{k=1}^{K}X_{ik}Z_{i}'(\hat{\alpha}_{k}-\hat{\alpha}_{0})]
    \\
    &    =
      % E_{n}[\hat{\Lambda}_{i}\hat{\Gamma}'Z_{i}]=
      E_{n}[\diag(\hat{\Lambda}_{i})\hat{\Gamma}'Z_{i}]+E_{n}[(\hat{\Lambda}_{i}-\diag(\hat{\Lambda}_{i}))\hat{\Gamma}'Z_{i}]
      =:\hbo+\hbcb,
  \end{split}
\end{equation}
where $\hat{\Gamma}$ is a matrix with columns
$\gamma_{k}=\alpha_{k}-\alpha_{0}$,
$\hat{\Lambda}_{i}=E_{n}[\dot{X}_{i}\dot{X}_{i}']^{-1}\dot{X}_{i}X_{i}'$, and
$E_{n}[A_{i}]=\sum_{i}\omega_{i}^{2}A_{i}/\sum_{i}\omega_{i}^{2}$ denotes the
weighted sample mean.

To compute this decomposition, we don't need to explicitly compute
$\hat{\Lambda}_{i}$. Instead, we use the identity
\begin{equation*}
  \hbo_{k}=e_{k}'E_{n}[\dot{X}_{i}\dot{X}_{i}']^{-1}E_{n}[\dot{X}_{i}X_{ik}Z_{i}'\hat{\gamma}_{k}]=\hat{\delta}_{k k}'
  \hat{\gamma}_{k},
\end{equation*}
where $\hat{\delta}_{k k}$ is a WLS estimator of the system of regressions
\begin{equation}\label{eq:delta_system}
  Z_{i}X_{ik}=\delta_{k k}X_{ik}+\sum_{\ell\neq k}\delta_{k \ell}X_{i\ell}
  +\Delta_{Z, k}Z_{i}+\zeta_{ik}.
\end{equation}

Note this decomposition and associated standard errors, in the next subsection, are purely
regression-based, so they remain valid even if $X_{i}$ is not a set of binary
indicators. Likewise, misspecification of the interacted regression only affects
the interpretation of the decomposition; if $\mu_k$ is not linear, the
decomposition will not consistently estimate the contamination bias.

The own treatment weights in this decomposition sum to one, and the
contamination weights sum to zero, since $E_{n}[\hat{\Lambda}_{i}]=I_{k}$,
mimicking the population decomposition. If the propensity score doesn't satisfy
$p_{k}\in\mathcal{G}$, the implied estimate of $\Lambda(w)$, \begin{equation*}
\hat{\Lambda}(w)=\frac{1}{n}\sum_{i=1}^{n}\1{W_{i}=w}\hat{\Lambda}_{i}
\end{equation*} may not be positive definite; in particular, the diagonal
elements may not all be positive, in line with Proposition 1 in @ghk23.

In addition to this decomposition, the package also computes the following
alternative estimators:

1. The unweighted ATE estimator, $\hbate_{k}=E_{n}[W_{i}]'\hat{\gamma}_{k}$
2. The one-treatment-at-a time estimator $\hbew_{k}$ that fits
   \eqref{eq:uninteracted_linear} using only observations with
   $D_{i}\in\{0,k\}$. In other words, it estimates the regression
   \begin{equation}\label{eq:1-at-a-time}
   Y_{i}=\ddot{\phi}_{k}+X_{ik}\ddot{\beta}_{k}+W_{i}^\prime\ddot{\phi}_{k}+
   \ddot{U}_{ik}, \end{equation} among observations with $D_{i}\in\{0,k\}$. This
   estimator weights the treatment effects using the variance-minimizing
   weighting scheme given in Corollary 1 in @ghk23. Consequently, we refer to as
   the efficiently weighted ATE estimator.
3. The common weights estimator $\hbcw$, given by the WLS regression of $Y_{i}$
   onto $X_{i}$, weighting each observation by \begin{equation*}
   \frac{\omega_{i}^{2}\pi_{D_{i}}(1-\pi_{D_{i}})}{\hat{p}_{D_{i}}(W_{i})\sum_{k=0}^{K}\hat{p}_{k}(W_{i})^{-1}},
   \end{equation*} where, by default, the probabilities $\pi_{k}$ correspond to
   the marginal probability $E_{n}[X_{ik}]$ in the dataset. The propensity
   scores $\hat{p}_{k}(W_{i})$ are based on fitting a multinomial logit model
   for the treatments. This estimator estimates a weighted ATE with weights
   $\lambda^{\text{CW}}(W_{i})=\left(\sum_{k=0}^{K}\frac{\pi_{k}(1-\pi_{k})}{p_{k}(W_{i})}\right)^{-1}$.
   By Corollary 2 in @ghk23, this weighting scheme minimizes the average
   variance, under homoskedasticity, across all treatment
   comparisons---comparisons of outcomes under treatment $k$ vs treatment
   $\ell$, if we draw the treatments $k$ and $\ell$ independently from the
   marginal treatment distribution $(\pi_{0},\dotsc,\pi_{K})$. Option
   `cw_uniform=TRUE` in the `multe` function sets these probabilities to $1/K$;
   setting the option to its default, `FALSE`, sets them to
   $(E_{n}[X_{i0}],\dotsc,E_{n}[X_{i K}])$.

## Standard errors

To compute cluster-robust standard errors for an asymptotically linear estimator
with influence function $\psi_{i}$, we use the formula
\begin{equation*}
  \widehat{\operatorname{se}}(\psi)^{2}=\frac{G}{G-1}\sum_{g}\left(\sum_{G_{i}= g}\psi_{i}\right)
  \left(\sum_{G_{i}= g}\psi_{i}\right)'.
\end{equation*}
Here $G_{i}$ denotes cluster membership, as specified by the `multe` argument
`cluster`, and $G$ the number of clusters. Specifying `cluster=NULL` assumes
independent data, setting each observation to be in its own cluster ($G_{i}=i$
and $G=N$), so the reported standard errors are robust to heteroskedasticity,
but not clustering.

We now describe the form of the influence function for the estimators above. For
a generic WLS regression of $A$ onto $B$, let
$(Q_{1},Q_{2}) \left(\begin{smallmatrix}
                       R & S\\
                       0 & 0
\end{smallmatrix}\right)\Pi'$ denote the QR decomposition of $\diag(\omega_{i})B$. If $B$
has rank $r$, then $R$ has dimension $r\times r$, $Q$ has dimension $N\times r$,
where $r$ is the rank of the regressor matrix, and $\Pi$ is a permutation
matrix. The WLS estimator is then given by $b=\Pi\left(\begin{smallmatrix}
                                                         R^{-1}Q_{1}'\diag(\omega_{i})A\\
                                                         \mathtt{NA}\end{smallmatrix}\right)$.
  Denoting the regression residual by $\hat{\epsilon}_{i}$, the influence
  function is thus given by
\begin{equation}\label{eq:psi_reg}
  \psi_{i}(b)=\Pi\left(\begin{smallmatrix}
                         R^{-1}Q_{1i}\omega_{i}\hat{\epsilon}_{i}\\
                         \mathtt{NA}\end{smallmatrix}\right).
\end{equation}
See the internal function `multe:::reg_if` for implementation. The
influence function for the inner product of linear estimators $a$ and $b$, is by
the delta method given by
  \begin{equation*}
    \psi_{i}(a' b)=a'\psi_{i}(b)+b'\psi_{i}(a),
  \end{equation*}
  while for scalars $s_{1},s_{2}$,
  $\psi(s_{1}a+s_{2}b)=s_{1}\psi(a)+s_{2}\beta(b)$.

We use \eqref{eq:psi_reg} to compute $\psi(\hat{\alpha}_{k})$, as well as
\begin{align*}
  \psi_{i}(\bar{Z})&=\frac{\omega_{i}^{2}(Z_{i}-\bar{Z})}{\sum_{i}\omega_{i}^{2}}\\
  \psi_{i}(\hat{\delta}_{k k})&=\frac{\omega_{i}^{2}\hat{\zeta}_{ik}\ddot{X}_{ik}}{\sum_{i}\omega_{i}^{2}\ddot{X}_{ik}^{2}},
\end{align*}
where $\hat{\zeta}_{ik}$ is the WLS residual based on
\eqref{eq:delta_system}, and $\ddot{X}_{ik}$ is the residual from regressing $X_{ik}$ onto $X_{i, -k}$ and
$Z_{i}$. It then follows from \eqref{eq:psi_reg} and the influence function
formulas above, that
\begin{align*}
  \psi_{i}(\hbo_{k})&=\hat{\delta}_{k k}'\psi_{i}(\hat{\gamma}_{k})+
                      \hat{\gamma}_{k}'\psi_{i}(\hat{\delta}_{k k})\\
  \psi_{i}(\hat{\beta})&=\left(\sum_{i}\omega_{i}^{2}\dot{X}_{i}\dot{X}_{i}'\right)^{-1}\omega_{i}^{2}\dot{X}_{i}\hat{U}_{i}\\
  \psi_{i}(\hbew_{k})&=\frac{\1{D_{i}\in\{0,k\}}
                                \omega_{i}^{2}\hat{X}_{ik}\hat{U}_{ik}}{\sum_{i}\1{D_{i}\in\{0,k\}}\omega_{i}^{2}\hat{X}_{ik}^{2}}\\
  \psi_{i}(\hbate_{k})&=\bar{Z}'\psi_{i}(\hat{\alpha}_{k}-\hat{\alpha}_{0})
                                +\psi_{i}(\bar{Z})(\hat{\alpha}_{k}-\hat{\alpha}_{0}).
\end{align*}
where $\hat{X}_{ik}$ is the residual from regressing $X_{ik}$ onto $Z$ in the
subset with $D_{i}\in\{0,k\}$, and $\hat{U}_{ik}$ the residual from regressing
$Y_{i}$ onto $X_{ik}$ and $Z_{i}$ in this subsample.

When the treatment is binary and overlap holds, the formula for
$\psi_{i}(\hbate_{k})$ is similar to that discussed on page 29 in
@imbens2009recent, except we don't assume that the regression error
$V_{i}$ in \eqref{eq:linear_mu} is conditionally mean zero, so that the standard
error is robust to misspecification.

Derivations in the last section show that the influence function for the common
weights estimator is given by
$\hat{\psi}_{i}(\hbcw_{k})=\hat{\psi}_{i}(\hat{\alpha}^{\textnormal{CW}}_{k}-\hat{\alpha}^{\textnormal{CW}}_{k})$, where
\begin{equation}\label{eq:psi_cw}
  \hat{\psi}_{i}(\hat{\alpha}^{\textnormal{CW}}_{k})=
  \frac{1}{\sum_{i}\lcw(W_{i})}\left(
    \frac{\lcw(W_{i})X_{ik}}{\pi_{k}(W_{i};\hat{\theta})}(Y_{i}-\hat{\alpha}^{\textnormal{CW}}_{k})
    +a_{i}(\hat{\theta})\right).
\end{equation}

with the formula for $a_i$ given in \eqref{eq:a_i} below, $\theta$ corresponds to
the parameters in the multinomial logit model, $\pi_{k}(W_{i};\hat{\theta})$ to the fitted
probabilities in this model, and $\hat{\alpha}^{\textnormal{CW}}_{k}$ is the
estimate based on \eqref{eq:moment_overlap_weights} below.

## Oracle standard errors

The package also reports "oracle" standard errors, which interprets the
alternative estimators as estimates of the contrasts
\begin{equation*}
  \beta_{\lambda,k}=\frac{\sum_{i=1}^{N}\lambda(W_{i})(\mu_{k}(W_{i})-\mu_{0}(W_{i}))}{\sum_{i=1}^{N}\lambda(W_{i})},
\end{equation*}
with $\lambda(W_{i})=1$ for the unweighted ATE, $\lambda(W_{i})=\lcw(W_{i})$ for
the common weights estimator and
$\lambda(W_{i})=\frac{p_{k}(W_{i})p_{0}(W_{i})}{p_{k}(W_{i})+p_{0}(W_{i})}$ for
the efficiently weighted ATE estimator. In contrast, the standard errors in the
previous subsection set the estimands to be the population counterparts to these
weighted averages, replacing the sums in the above display with population
expectations. In addition, the oracle standard errors don't account for
estimation error in the propensity score $p(W_{i})$.

For the unweighted ATE, the oracle standard error is based on the influence
function
$\tilde{\psi}_{i}(\hat{\beta}_{k}^{ATE})=\bar{Z}'\psi_{i}(\hat{\alpha}_{k}-\hat{\alpha}_{0})$.
From the derivation in the last section, it follows that the oracle standard
error for  $\hbew_{k}$ is given by
\begin{equation}\label{eq:hbew_oracle}
  \psi_{i}(\hbew_{k})=\frac{\1{D_{i}\in\{0,k\}}
    \omega_{i}^{2}\hat{X}_{ik}\hat{\dot{U}}_{i}}{\sum_{i}\1{D_{i}\in\{0,k\}}\omega_{i}^{2}\hat{X}_{ik}^{2}},
\end{equation}
where $\hat{\dot{U}}_{i}$ is the interacted regression residual based on \eqref{eq:linear_mu}.

Finally, the oracle standard errors for $\hbcw_{k}$ are based on the influence
function
$\tilde{\psi}_{i}(\hbcw_{k})=\tilde{\psi}_{i}(\hat{\alpha}^{\text{CW}}_{k})-\tilde{\psi}_{i}(\hat{\alpha}^{\text{CW}}_{0})$,
where
\begin{equation}\label{eq:overlap_oracle}
  \tilde{\psi}_{i}(\hat{\alpha}^{\text{CW}}_{k})=\frac{\omega_{i}^{2}\lcw(W_{i};\hat{\theta})}{
    \sum_{i}\omega_{i}^{2}\lcw(W_{i};\hat{\theta})}\frac{X_{ik}}{\pi_{k}(W_{i};\hat{\theta})}\hat{\dot{U}}_{i}.
\end{equation}

## Overlap sample

The package applies the above formulas to the full sample. In cases with poor
overlap, this may not yield well-defined estimates or bias decomposition for all
treatments. For components of the decomposition and alternative estimators that
are not identified, the package returns `NA`. In such cases, the package also
returns results for a trimmed "overlap sample", where the decomposition and
alternative estimators are all identified. The overlap sample is constructed as
follows:

1. Find a factor variable among the controls with the greatest number of levels.
   If there are no factor variables, skip this step. If for some levels of this
   variable, we don't see observations that take on one or more of the $K+1$
   possible treatments, drop observations with these levels.
2. For the remaining controls, if a control doesn't display any variation in the
   subset of the data with treatment $k=0,\dotsc,K$, drop the control.


## Wald and LM tests

We now give the form of the Wald and LM tests for variation in the propensity
score. First, we give a general derivation of these tests in a
likelihood context when the Hessian may be reduced rank. We then specialize the
formulas to the case where the likelihood corresponds to the that for the
multinomial logit model.

Consider a log-likelihood $\ell_{n}(\theta)$ for a $p$-dimensional parameter
$\theta$, with score function $S$ that's approximately normal with covariance
matrix $\Omega$, and Hessian $H$. We're interested in testing the hypothesis
that last $r$ elements of $\theta$ are zero, $H_{0}\colon \theta_{2}=0$. We
assume that the submatrix $H_{11}$ of the Hessian corresponding to the
restricted model is full rank, but the full matrices $\Omega$ or $H$ may not be
invertible.

The score evaluated at the unrestricted estimator $\hat{\theta}$ satisfies
\begin{equation*}
  0=
  \begin{pmatrix}
    S_{1}(\hat{\theta}_{1},\hat{\theta}_{2})\\
    S_{2}(\hat{\theta}_{1},\hat{\theta}_{2})
  \end{pmatrix}=
  \begin{pmatrix}
    S_{1}(\theta_{1},0)\\
    S_{2}(\theta_{1},0)
  \end{pmatrix}+
  \begin{pmatrix}
    H_{11}(\hat{\theta}_{1}-\theta_{1}) + H_{12}\hat{\theta}_{2}\\
    H_{21}(\hat{\theta}_{1}-\theta_{1}) + H_{22}\hat{\theta}_{2},
  \end{pmatrix}
\end{equation*}
ignoring in the notation that the Hessian evaluated needs to be evaluated at
intermediate values. Rearranging,
\begin{equation*}
  \begin{pmatrix}
    \hat{\theta}_{1}-\theta_{1}\\
    (H_{22}-H_{21}H_{11}^{-1}H_{12})\hat{\theta}_{2}
  \end{pmatrix}
=
\begin{pmatrix}
  -H_{11}^{-1}S_{1}(\theta_{1},0)-H_{11}^{-1}H_{12}\hat{\theta}_{2}\\
  H_{21}H_{11}^{-1}S_{1}(\theta)-S_{2}(\theta)
\end{pmatrix}
\end{equation*}
This yields the Wald statistic
\begin{equation*}
  W=\hat{\theta}_{2}'(H_{22}-H_{21}H_{11}^{-1}H_{12})'
  \operatorname{var}(S_{2}(\theta_{1},0)-H_{21}H_{11}^{-1}S_{1}(\theta_{1},0))^{+}
  (H_{22}-H_{21}H_{11}^{-1}H_{12})\hat{\theta}_{2},
\end{equation*}
where $A^{+}$ denotes a generalized inverse. By Lemma 9.7 in @NeMc94, the
statistic has an asymptotic $\chi^{2}$ distribution with degrees of freedom
equal to the rank of the variance.

The score evaluated at the restricted estimator $\bar{\theta}_{1}$ satisfies
\begin{equation*}
  \begin{pmatrix}
    0\\
    S_{2}(\bar{\theta}_{1},0)
  \end{pmatrix}=
  \begin{pmatrix}
    S_{1}(\theta_{1},0)\\
    S_{2}(\theta_{1},0)
  \end{pmatrix}+
  \begin{pmatrix}
    H_{11}(\bar{\theta}_{1}-\theta_{1})\\
    H_{21}(\bar{\theta}_{1}-\theta_{1})
  \end{pmatrix},
\end{equation*}
which implies
$\bar{\theta}_{1}-\theta_{1}=-H_{11}^{-1}S_{1}(\theta_{1},0)$, and hence
\begin{equation*}
  S_{2}(\bar{\theta}_{1},0)
  =S_{2}(\theta_{1},0)-H_{21}H_{11}^{-1}S_{1}(\theta_{1},0).
\end{equation*}
Thus the statistic
\begin{equation*}
  LM=S_{2}(\bar{\theta}_{1},0)'\operatorname{var}(S_{2}(\theta_{1},0)-H_{21}H_{11}^{-1}S_{1}(\theta_{1},0))^{+}
  S_{2}(\bar{\theta}_{1},0)
\end{equation*}
will again have a $\chi^{2}$ distribution.

To apply these formulas in the context of a multinomial logit model, we use the
score and the Hessian
\begin{equation*}
  S(\theta)=  \sum_{i}\omega^{2}_{i}(X_{i}-\pi(Z_{i};\theta))\otimes Z_{i},\quad
  H(\theta)=
  -\sum_{i}\omega^{2}_{i}(\diag(\pi(Z_{i};\theta))-\pi(Z_{i};)\pi(Z_{i})')\otimes Z_{i}Z_{i}'
\end{equation*}

# Derivations

*We first derive \eqref{eq:psi_cw}*. Observe first that the common weights
estimator is identical to the two-step GMM estimator that in the first step,
fits a multinomial logit model
\begin{equation}\label{eq:m-n-l}
  P(D_{i}=k\mid W_{i})=\frac{e^{Z_{i}'\theta_{k}}}{\sum_{k'=0}^{K}e^{Z_{i}'\theta_{k'}}}=:  \pi_{k}(W_{i},\theta),
\end{equation}
with the normalization $\theta_{0}=0$. In the second step, we use the moment condition
\begin{equation}\label{eq:moment_overlap_weights}
  E\left[\frac{\lcw(W_{i};\theta)X_{ik}}{\pi_{k}(W_{i};\theta)}(Y_{i}-\alpha^{\text{CW}}_{k})\right]=0.
\end{equation}
to obtain estimates $\hat\alpha^{\text{CW}}_{k}$, and set $\hbcw_k=\hat\alpha^{\text{CW}}_{k}-\hat\alpha^{\text{CW}}_{0}$.

Let
\begin{equation*}
 \zeta_{k}(W_{i};\hat{\theta})=\frac{\lcw(W_{i};\hat{\theta})}{\pi_{k}(W_{i},\hat{\theta})}
  % =\frac{1}{\pi_{k}(W_{i},\hat{\theta})\sum_{k'=0}^{K}\frac{\pi_{k'}(1-\pi_{k'})}{\pi_{k}(W_{i};\hat{\theta})}}
  =\frac{e^{-Z_{i}'\hat{\theta}_{k}}}{\sum_{j=0}^{K}\pi_{j}(1-\pi_{j})e^{-Z_{i}'\hat{\theta}_{j}}}
\end{equation*}
By equation (6.6) in @NeMc94, the influence function of this two-step
estimator is given by
\begin{equation*}
\psi_{i}(\hat{\alpha}^{\textnormal{CW}}_{k})=  \frac{1}{E[\lcw(W_{i})]}\left(
\frac{\lcw(W_{i})X_{ik}}{\pi_{k}(W_{i})}(Y_{i}-\alpha^{\text{CW}}_{k})
+M_{k}(\theta)\psi_{i}(\theta)\right),
\end{equation*}
where $\psi_{i}(\theta)$ is the influence function of the multinomial logit
estimator $\hat{\theta}$, and $M_{k}(\theta)$ is the derivative of
\eqref{eq:moment_overlap_weights} wrt $\theta$.

Since
$\partial \zeta_{k}(W_{i};\theta)/\partial \theta_{j}=
Z_{i}\zeta_{k}(W_{i};\theta)[\pi_{j}(1-\pi_{j})\zeta_{k}(W_{i};\theta)-\1{k=j>0}]$, it follows that
\begin{equation*}
  M_{k}(\theta)=
E[(\eta-e_{k})\otimes Z_{i}\cdot \zeta_{k}X_{ik}(Y_{i}-\alpha_{\lambda^{C},k})],\qquad\eta=(
\pi_{j}(1-\pi_{j})\zeta_{j}, \dotsc,\pi_{K}(1-\pi_{K})\zeta_{K})'.
\end{equation*}
Since the multinomial logit log-likelihood is given by
$\ell_{i}=\sum_{k=0}^{K}X_{k}\log(\pi_{k})=\sum_{k=0}^{K}X_{k}Z_{i}'\theta_{k}
-\log(\sum_{k=0}^{K}e^{Z_{i}'\theta_{k}})$, the score and the Hessian are
\begin{equation*}
  S_{i}(\theta)=(X_{i}-\pi(W_{i};\theta))\otimes Z_{i},\qquad
  H(\theta)=-E_{n}[(\diag(\pi(W_{i}))-\pi(W_{i})\pi(W_{i})')\otimes Z_{i}Z_{i}'],
\end{equation*}
Since $\psi_{i}(\theta)=-H(\theta)^{-1}S_{i}(\theta)$, this yields
\begin{equation}\label{eq:a_i}
  a_{i}(\theta)=\hat{M}_{k}(\hat{\theta})
  \hat{H}(\hat{\theta})^{-1}S_{i}(\theta),
  \qquad S_{i}(\theta)=
  (X_{i}-\pi(W_{i};\theta))\otimes Z_{i},
\end{equation}
with $\hat{M}_{k}({\theta})=\left(\sum_{i}(\zeta-e_{k})\otimes Z_{i}\cdot
  \zeta_{k}X_{ik}(Y_{i}-\alpha_{\lambda^{C},k})\right)$, and $\hat{H}({\theta})=
  \sum_{i}(\diag(\pi(W_{i}))-\pi(W_{i})\pi(W_{i})')\otimes Z_{i}Z_{i}'$.
When $\pi_k=1/(K+1)$ this formula reduces to that in Theorem 1 in @lili19.

*Next, we show \eqref{eq:hbew_oracle}*. Note that it follows from Proposition 2 in
@ghk23 that the efficient influence function is given by
\begin{multline*}
  \psi_{i}({\alpha}_{\lambda_{k},k0})=
  \frac{\lambda(W_{i})}{E[\lambda(W_{i})]}\left(\frac{X_{ik}}{p_{k}(W_{i})}(Y_{i}-\mu_{k}(W_{i}))
    -  \frac{X_{i0}}{p_{0}(W_{i})}(Y_{i}-\mu_{0}(W_{i}))\right)\\
  =  \frac{X_{ik}+X_{i0}}{E[\lambda(W_{i})]}\left(X_{ik}-r_{k}\right)V_{i}=
  \frac{(X_{ik}+X_{i0})(X_{ik}-r_{k})V_{i}}{E[(X_{ik}+X_{i0})(X_{ik}-r_{k})^{2}]},
\end{multline*}
where $r_{k}=r_{k}(W_{i})=E[X_{ik}\mid W_i,X_{ik}+X_{i0}=1]$. The result then follows
since $\hat{X}_{ik}$ is an estimator of $X_{ik}-r_{k}(W_{i})$.

*Finally, we show \eqref{eq:overlap_oracle}*. The derivative of the moment condition
\eqref{eq:moment_overlap_weights} with respect to $\pi_{k}=p_{k}$ (assuming
correct specification of the propensity score) is given by
\begin{equation*}
  -E[\lambda\frac{X_{ik}}{p_{k}^{2}(W_{i})} (\mu_{k}-\alpha^{\text{CW}}_{k})\dot{p}_{k}(W_{i})],
\end{equation*}
where we write $\lambda$ for $\lcw(W_{i})$. Since $p_{k}$ is a projection, by
Proposition 4 in @newey94ecta, the influence function for
$\hat{\alpha}^{\text{CW}}_{k}$ is given by
\begin{multline*}
  \frac{1}{E[\lambda]}\left(  \lambda \frac{X_{ik}}{p_{k}(W_{i})}(Y_{i}-\alpha^{\text{CW}}_{k})
    -\frac{\lambda}{p_{k}(W_{i})}(\mu_{k}(W_{i})-\alpha^{\text{CW}}_{k})(X_{ik}-p_{k}(W_{i}))\right)\\
  =
  \frac{1}{E[\lambda]}\left(  \lambda\frac{X_{ik}}{p_{k}(W_{i})}(Y_{i}-\mu_{k}(W_{i}))
    +  \lambda(\mu_{k}(W_{i})-\alpha^{\text{CW}}_{k})
\right).
\end{multline*}
Next, as noted in @AbImZh14, we can view
$\tilde{\alpha}^{\text{CW}}_{k}=\sum_{i}\lambda\mu_{k}(W_{i})/\sum_{i}\lambda$ as an estimator of
${\alpha}^{\text{CW}}_{k}$ based on the moment condition
$E[\lambda(\mu_{k}(W_{i})-{\alpha}^{CW}_{k})]=0$, which by standard
arguments has influence function given by
$\frac{\lambda}{E[\lambda]}(\mu_{k}(W_{i})-{\alpha}^{\text{CW}}_{k})$. Since
$\hat{\alpha}^{\text{CW}}_{k}-\alpha^{CW}_{k}=(\hat{\alpha}^{\text{CW}}_{k}-{\alpha}^{\text{CW}}_{k})-({\alpha}^{\text{CW}}_{k}
-\tilde{\alpha}^{\text{CW}}_{k})$,
we subtract this influence function from the preceding display to obtain \eqref{eq:overlap_oracle}.


# References
